Figure 1c

### 2017-11-21 inst/tcga_correlation/tcga_correlation.Rmd
tcga correlation plotting done

---
title: "Figure 1c"
subtitle: "miR34a asRNA and miR34a TCGA correlation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

####_Results_

@@

```{r, out.width = "1000px"}

url <- fileMap(type = "png")["figure1c"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

>>>>

---
title: "Figure 1c"
subtitle: "miR34a asRNA and miR34a TCGA correlation"
author: "Jimmy Van den Eynden and Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

####_Results_
```{r}
url <- fileMap(type = "rds")["figure1c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#normalize expression values
data <- mutate(
    data,
    RP3 = log2(RP3 / max(RP3)),
    miR34a = log2(miR34a / max(miR34a))  
  )

#add BRCA subtypes
data <- data %>%
  mutate(PAM50 = if_else(is.na(PAM50), "", PAM50)) %>%
  mutate(cancer_PAM50 = gsub("BRCA", "BRCA ", paste(cancer, PAM50, sep = "")))
```

```{r, fig.align='center', fig.height=8, fig.width=12, message = FALSE}
#plot
data %>%
  arrange(cancer_PAM50, TP53, RP3) %>%
  plotTCGAcorrelation(type = "diploid only")

#save to pdf
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
pdf(path, width = 28)
data %>%
  arrange(cancer_PAM50, TP53, RP3) %>%
  plotTCGAcorrelation(type = "diploid only")
dev.off()

@@
